---
title: "Snpnet Vignette"
author: "Junyang Qian, Yosuke Tanigawa, and Trevor Hastie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Introduction

### A Simple Example

```{r}
library(multisnpnet)
```

```{r, results='hide', message=FALSE, warning=FALSE}
fit_multisnpnet <- multisnpnet(
    genotype_file = genotype_file,
    phenotype_file = phenotype_file,
    phenotype_names = phenotype_names,
    covariate_names = covariate_names,
    #   results_dir = results_dir,
    rank = r,
    batch_size = batch_size,
    split_col = split.col,
    max.iter = max.iter,
#      thresh = thresh,
    configs = configs,
    lambda.min.ratio = lambda.min.ratio,
    nlambda = nlambda,
    standardize_response = standardize_response,
    save = save,
    validation = validation,
    prev_iter = prev_iter,
    early_stopping = early_stopping,
    # glmnet_thresh = thresh,
    weight = weight,
    mem = mem
)
```

### Example of Biplot Visualization

The coefficent matrix $C$ in the returned value from `multisnpnet::multisnpnet()` has the dimension of $p \timex q$. One can visualize this matrix with a biplot visualization.

```{r}
plot_biplot(
    svd(t(fit_multisnpnet$C)),
    label=list(
        'phenotype'=rownames(A_init), # we should update this phenotype labels so that it matches with the simple example above.
        'variants'=rownames(fit$C)
    )
)
```

By default, this function annotates 5 phenotypes and 5 variants based on the distance from the center of origin. One can annotate more points by specifying `n_labels` option.

Alternatively, you can generate an interactive plot with `plotly` with mouseover annotation of phenotypes and variants. In that case, you need to disable the static annotation by specifying `use_ggrepel=FALSE`.

```{r}
if (!require('plotly', character.only = TRUE)) {
    install.packages('plotly', dependencies = TRUE)
    library('plotly', character.only = TRUE)
}

plot_biplot(
    svd(t(fit_multisnpnet$C)),
    label=list(
        'phenotype'=rownames(A_init), # we should update this phenotype labels so that it matches with the simple example above.
        'variants'=rownames(fit$C)
    ),
    use_ggrepel=FALSE
) %>%
plotly::ggplotly() %>%
htmlwidgets::saveWidget('multisnpnet.biplot.html', selfcontained = F, libdir = "lib")
```

You can open the resulting html file (`multisnpnet.biplot.html`) with your favorite browser.
